### 2019-12-05 paper6/article.tex
paper 6 refs added.

We study the effective slip over microcavities partially filled with a second fluid using the parameters summarized in Tab.\ \ref{tab: param}.
%by varying the viscosity ratio $\tilde{\mu}_2/\tilde{\mu}_1$, the capillary number $Ca=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$, the static contact angle $\theta_s$, and the \Ge{filling fraction} of the cavity \Ge{$\delta=2d_0/H$}. The contact line velocity is obtained from the local phase field model, using the physical properties of the two fluids as summarized in Tab.\ \ref{tab: param}. 
Here, six pairs of fluids are considered as in the experiment \cite{Solomon}, leading to a wide range of $\tilde{\mu}_2/\tilde{\mu}_1$ from $31.7$ to $3.83\e{-3}$. \Ge{The filling fraction is initialized to $\delta=0.94$ (corresponding to a depth $d_0=0.47H$) to allow for some sloshing of the lubricant.} The velocity ratio $\chi=\tilde{U}_c/ (\dot{\tilde{\gamma}} \tilde{H})$ is set constant for all the fluid pairs and shear rates to reduce the number of parameters and focus on the single physical effects mentioned above. This also implies that the capillary number is varied by changing the outer fluid viscosity. As an example, for $\dot{\tilde{\gamma}}=800$ s$^{-1}$, $\tilde{H}=20$ $\mu$m, and $\tilde{U}_c=2.63$ m/s (see \cite{dimension} for the detailed estimation), the velocity ratio $\chi \approx 164$ (which is indeed much greater than 1), and the corresponding Ca increases from $1.92\e{-3}$ to $1.59$ for the different viscosities considered. We further modify Ca at a fixed $\chi$ to study the effect of interface deformation. Finally, the effect of the static contact angle is investigated by considering $\theta_s=80\degree$ (leading to a convex meniscus), $\theta_s=105\degree$ (concave meniscus), \Ge{and $\chi u_c(\theta)=0 $ for $\theta_s \in [76\degree, 84\degree ]$ to mimic some contact angle hysteresis.}

@@

%--%%Wetting on nanorough surfaces,

>>>>

We study the effective slip over microcavities partially filled with a second fluid using the parameters summarized in Tab.\ \ref{tab: param}.
%by varying the viscosity ratio $\tilde{\mu}_2/\tilde{\mu}_1$, the capillary number $Ca=\tilde{\mu}_1 \dot{\tilde{\gamma}} \tilde{H}/\tilde{\sigma}$, the static contact angle $\theta_s$, and the \Ge{filling fraction} of the cavity \Ge{$\delta=2d_0/H$}. The contact line velocity is obtained from the local phase field model, using the physical properties of the two fluids as summarized in Tab.\ \ref{tab: param}. 
Here, six pairs of fluids are considered as in the experiment \cite{Solomon}, leading to a wide range of $\tilde{\mu}_2/\tilde{\mu}_1$ from $31.7$ to $3.83\e{-3}$. \Ge{The filling fraction is initialized to $\delta=0.94$ (corresponding to a depth $d_0=0.47H$) to allow for some sloshing of the lubricant.} The velocity ratio $\chi=\tilde{U}_c/ (\dot{\tilde{\gamma}} \tilde{H})$ is set constant for all the fluid pairs and shear rates to reduce the number of parameters and focus on the single physical effects mentioned above. This also implies that the capillary number is varied by changing the outer fluid viscosity. As an example, for $\dot{\tilde{\gamma}}=800$ s$^{-1}$, $\tilde{H}=20$ $\mu$m, and $\tilde{U}_c=2.63$ m/s, 
%(see \cite{dimension} for the detailed estimation), 
the velocity ratio $\chi \approx 164$ (which is indeed much greater than 1), and the corresponding Ca increases from $1.92\e{-3}$ to $1.59$ for the different viscosities considered.\footnote{We estimate the dimensional shear rate at the upper boundary of our computational domian from the experimental Hele-Shaw setup in \cite{Wexler} (2 mL/min through a cross-section of 180 $\mu$m $\times$ 7 mm). Assuming a parabolic velocity profile, the reference velocity at $\tilde{H}=20$ $\mu$m is $\tilde{U}=$ 0.016 m/s, leading to a shear rate of $\dot{\tilde{\gamma}}=800$ s$^{-1}$. The characteristic contact line velocity is calculated as $\tilde{U}_c=\tilde{\sigma}/\tilde{\mu}_2$, taking $\tilde{\sigma}=0.02$ kg/$s^2$ and $\tilde{\mu}_2=0.0076$ $\nicefrac{kg}{ms}$, as in \cite{Martin}} We further modify Ca at a fixed $\chi$ to study the effect of interface deformation. Finally, the effect of the static contact angle is investigated by considering $\theta_s=80\degree$ (leading to a convex meniscus), $\theta_s=105\degree$ (concave meniscus), \Ge{and $\chi u_c(\theta)=0 $ for $\theta_s \in [76\degree, 84\degree ]$ to mimic some contact angle hysteresis.}

@@

%--%%Wetting on nanorough surfaces,c
